A prototype software framework for transparent, reusable and updatable computational health economic models

### 2023-10-23 Markdown/Manuscript/Child_RMDs/Clippings.Rmd
built submission files

<!-- Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework. To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995]. Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features. We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service. We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model. Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts. Progress is reported on a project website [@rfwn2022]. -->

>>>>

<!-- Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework. To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995]. Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features. We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service. We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model. Our initial work on *readyforwhatsnext* is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts. Progress is reported on a project website [@rfwn2022]. -->

### 2023-10-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
built submission files

(i) **establish socially acceptable user requirements and design specifications** (during CHEM planning);

(ii) **ensure fitness for purpose** (of CHEM implementation); and

(iii) **support socially beneficial use** (on CHEM release).

@@

Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].  The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975]. For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs when agreeing CHEM **user requirements and design specifications**. These trade-offs in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).

@@

Modellers have duties both to ensure a computational model is **fit for purpose** and to provide potential third-party users with the means of assessing its adequacy for their proposed uses [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068]. However, it is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020]. Appropriate computational implementation choices can help address many of these shortcomings, for example by automating quality assurance checks and facilitating manual reviews by third parties.

A CHEM will have limited **social benefit** if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay. Reuse of CHEMs as components of other models can potentially make model development more efficient [@Arnold2010; @garcia2021cost]. However, health economic models face challenges related to transferability across jurisdictions [@garcia2021cost] that create barriers to reuse. Without ongoing maintenance, a CHEM risks becoming less reliable with time [@garcia2021cost] and is at risk of being deployed for purposes for which it is poorly suited [@calder2018computational]. Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates [@Sampson2017], thus limiting the temporal window within which a CHEM can be validly applied. 
<!-- Reuse of models as components of other models can also make model implementation more efficient [@Arnold2010; @garcia2021cost] but the reusability of models is significantly shaped by computational implementation choices such as how model code and data are authored, documented, licensed and disseminated.  -->

@@

Taking steps to make computational models **transparent** is an important part of ethical public health modelling practice [@10.3389/fpubh.2017.00068]. Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented [@Eddy2012]. Notably, the same guidelines, published over ten years ago, do not recommend sharing model code and data. However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts [@Erdemir2020]. Online repository services such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection. Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance [@techver2019]. The extensiveness of such verification checks can be reported using the concept of code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested. Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape]. This issue can be addressed by use of online repository services such as GitHub [@github2007], that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.

A CHEM that is **reusable** also signals ethical modelling practice. Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.  Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse. Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify. Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular]. The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models. Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used. Alternatively, copyleft licenses [@copyleft2022] can be used to require that derivative works created by content users remain open-source. 
<!-- Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to -->
<!-- Using open-source development platforms and licenses can aid both generalizability and transferability. -->
<!-- The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.  -->
<!-- are relatively easier to selectively modify. -->

Models should be **updatable** so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost]. Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay [@calder2018computational]. Sustainable maintenance of open source research software requires both a core development team and an active user community [@info:doi/10.2196/20028]. Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements. Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable. It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of continuous integration [@CI2017].  The risk of software revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated CHEMs.
<!-- Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project. For more complex and multi-purpose CHEMs, particularly those designed to be incorporated into decision support systems, it may be better for development teams to adopt Agile Software Development [@beck2001manifesto], an approach that has been recommended for complex public health software projects [@10.3389/fpubh.2022.899874]. An Agile model will be less clearly specified in the initial project plan, but will instead continually develop in response to the requirements and feedback of users, who are provided with an initial, simplified working version of the model at the earliest feasible opportunity. -->

@@

How **transparent** a CHEM is can be assessed against the criteria:

-	**T1**: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.

-	**T2**: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.

How **reusable** a CHEM is can be assessed against the criteria:

-	**R1**: Programming practices facilitate both generalisability and transferability.

-	**R2**: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.

How **updatable** a CHEM is can be assessed against the criteria:

-	**U1**: Maintenance infrastructure is in place to support version control and collaboration with model users.

-	**U2**: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.

>>>>

(i) *establish socially acceptable user requirements and design specifications* (during CHEM planning);

(ii) *ensure fitness for purpose* (of CHEM implementation); and

(iii) *support socially beneficial use* (on CHEM release).

@@

Misalignment between the values of computational model developers and those of the population groups affected by decisions based on their models presents significant ethical risks [@thompson2022escape; @duckett2022journey].  The value judgments of health economic modellers are rarely adequately specified, omissions that may lead to socially unacceptable policy recommendations [@duckett2022journey]. These value judgments influence the assumptions, selection of model features and standards for evidence that shape health economic model projects [@HARVARD2020112975]. For example, as illustrated in Table \@ref(tab:proscons), project resource constraints may require model developers to make trade-offs when agreeing CHEM *user requirements and design specifications*. These trade-offs in turn determine how straightforward it is for a CHEM to be subsequently amended to reflect alternative value judgments relating to model conceptualisation and mathematical formalisation (Table \@ref(tab:timelygls)).

@@

Modellers have duties both to ensure a computational model is *fit for purpose* and to provide potential third-party users with the means of assessing its adequacy for their proposed uses [@Erdemir2020; @Feenstra2022; @thompson2019escape; @10.3389/fpubh.2017.00068]. However, it is common for health economic models to have serious methodological flaws [@carletto_zanuzzi_sammarco_russo_2020; @WONDER2015467]; insufficient validation [@Ghabri2019; @kolovos2017model; @haji2013model], poor reproducibility [@Jalali2021; @McManus2019; @Bermejo2017]; and undeclared errors [@Radeva2020]. Appropriate computational implementation choices can help address many of these shortcomings, for example by automating quality assurance checks and facilitating manual reviews by third parties.

A CHEM will have limited *social benefit* if it is rarely used, if mis-used or when its acceptability and adequacy rapidly decay. Reuse of CHEMs as components of other models can potentially make model development more efficient [@Arnold2010; @garcia2021cost]. However, health economic models face challenges related to transferability across jurisdictions [@garcia2021cost] that create barriers to reuse. Without ongoing maintenance, a CHEM risks becoming less reliable with time [@garcia2021cost] and is at risk of being deployed for purposes for which it is poorly suited [@calder2018computational]. Currently, health economic models are rarely implemented computationally in a manner that facilitates routine updates [@Sampson2017], thus limiting the temporal window within which a CHEM can be validly applied. 
<!-- Reuse of models as components of other models can also make model implementation more efficient [@Arnold2010; @garcia2021cost] but the reusability of models is significantly shaped by computational implementation choices such as how model code and data are authored, documented, licensed and disseminated.  -->

@@

Taking steps to make computational models *transparent* is an important part of ethical public health modelling practice [@10.3389/fpubh.2017.00068]. Guidance on transparency in health economic modelling recommend that model code and data should be clearly documented [@Eddy2012]. Notably, the same guidelines, published over ten years ago, do not recommend sharing model code and data. However, more recent healthcare modelling guidance does recommend public dissemination of such artefacts [@Erdemir2020]. Online repository services such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection. Ensuring that calculations are correct and consistent with model specifications is an essential part of CHEM quality assurance [@techver2019]. The extensiveness of such verification checks can be reported using the concept of code coverage [@ERICWONG2010188] - the proportion of model code that has been explicitly tested. Tests should ideally combine both unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). The nature and extent of individual model authorship contributions can become unclear when models are implemented over longer time-frames with a large and changing group of collaborators [@thompson2022escape]. This issue can be addressed by use of online repository services such as GitHub [@github2007], that provide citation tools and can transparently record all individual code contributions to a modelling project over its lifecycle.

A CHEM that is *reusable* also signals ethical modelling practice. Although making a CHEM’s code, data and documentation publicly available is increasingly considered good practice, it is insufficient to enable model re-use.  Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Writing model algorithms as collections of functions (short, self-contained and reusable software routines that each perform a discrete task) is good scientific computing practice [@Wilson_2017] and promotes selective reuse. Computational implementations that store model code and data in distinct files and locations (as opposed to embedding data such as parameter values into source code) are easier to selectively modify. Modular implementations enable models to be constructed from multiple independently reusable and replaceable sub-models (modules) [@pan2021modular]. The programming concept inheritance [@8717448], deployed in object-oriented programming approaches, can facilitate the duplication and selective modification of models. Granting permissions to others to use, test and adapt models and their components, can be facilitated by two broad categories of open source licenses. Some guidance strongly recommends the use of permissive licensing [@Wilson_2017] that provides users with great flexibility as to the purposes (including commercial) for which content can be re-used. Alternatively, copyleft licenses [@copyleft2022] can be used to require that derivative works created by content users remain open-source. 
<!-- Compared to using commercial modelling software, authoring CHEMs in an open-source language like R [@RCORE2022] makes it easier to -->
<!-- Using open-source development platforms and licenses can aid both generalizability and transferability. -->
<!-- The choices that CHEM developers make about model implementation and licensing will also shape who can use a model and for what purposes.  -->
<!-- are relatively easier to selectively modify. -->

Models should be *updatable* so that they remain valid for longer, evolving as new evidence emerges and the systems being modelled change [@Jenkins2021; @garcia2021cost]. Ensuring that a model is regularly reviewed to identify and implement required improvements is a recommended defence against model validity decay [@calder2018computational]. Sustainable maintenance of open source research software requires both a core development team and an active user community [@info:doi/10.2196/20028]. Online communities can be an efficient means of engaging model users in testing each version of a model, identifying issues and suggesting improvements. Services such as GitHub [@github2007] provide collaborative code development tools [@MERGEL2015464] that help elicit, integrate and reconcile contributions from multiple contributors and to ensure each update is uniquely identifiable and retrievable. It is also important that verification checks are rerun with each model update, a task that can be automated using the software development practice of continuous integration [@CI2017].  The risk of software revisions having unintended consequences for third party users can be mitigated through the use of deprecation conventions [@zhou2016api] that take an informative and staged approach to retiring outdated CHEMs.
<!-- Currently, the core development team for a CHEM will be typically be funded to produce a project end-point deliverable whose specifications are well defined early in the project. For more complex and multi-purpose CHEMs, particularly those designed to be incorporated into decision support systems, it may be better for development teams to adopt Agile Software Development [@beck2001manifesto], an approach that has been recommended for complex public health software projects [@10.3389/fpubh.2022.899874]. An Agile model will be less clearly specified in the initial project plan, but will instead continually develop in response to the requirements and feedback of users, who are provided with an initial, simplified working version of the model at the earliest feasible opportunity. -->

@@

How *transparent* a CHEM is can be assessed against the criteria:

-	*T1*: Software files (executable code, testing procedures and outcomes and non-confidential data) are available in open access repositories.

-	*T2*: It is easy to see who funded, developed and tested each part of the CHEM and to identify the modelling team’s assumptions, judgments and theories about CHEM development and use.

How *reusable* a CHEM is can be assessed against the criteria:

-	*R1*: Programming practices facilitate both generalisability and transferability.

-	*R2*: Licenses restrict only unethical use and allow anyone to ethically reuse model code and non-confidential data, in whole or in part, without charge, and for purposes that include the creation of derivative works.

How *updatable* a CHEM is can be assessed against the criteria:

-	*U1*: Maintenance infrastructure is in place to support version control and collaboration with model users.

-	*U2*: Each new release of a CHEM is systematically retested, with changes implemented to minimise disruptions for existing model users.

### 2023-10-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
built submission files

One framework library provides a **foundation for modular CHEM implementations**. In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering]. To achieve this, the foundation framework library defines a template CHEM module (using R’s S4 class system), which can be used to create other CHEM modules with a common set of inherited properties. One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named. The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with the framework and tools for partially automating updates to a project documentation website.

Three framework libraries are designed to help streamline and standardise workflows for **authoring CHEM modules** from the template module. The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library. One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. A second module authoring library contains tools to help streamline and standardise the authoring and documenting of novel CHEM modules. A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:

@@

A library for **managing CHEM data** contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories. A library for **authoring reproducible analyses** contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses. These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).

>>>>

One framework library provides a *foundation for modular CHEM implementations*. In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering]. To achieve this, the foundation framework library defines a template CHEM module (using R’s S4 class system), which can be used to create other CHEM modules with a common set of inherited properties. One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named. The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with the framework and tools for partially automating updates to a project documentation website.

Three framework libraries are designed to help streamline and standardise workflows for *authoring CHEM modules* from the template module. The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library. One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. A second module authoring library contains tools to help streamline and standardise the authoring and documenting of novel CHEM modules. A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:

@@

A library for *managing CHEM data* contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories. A library for *authoring reproducible analyses* contains tools to help write programs that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses. These analysis programs can be either self-documenting (code is integrated with plain English explanations of what it does) or trigger the creation of explanatory documents (e.g., a scientific manuscript).

### 2023-10-23 Markdown/Manuscript/Parent_PDF/Springer.Rmd
built submission files

title: A prototype software framework for transparent, reusable and updatable computational health economic models
titlerunning: Transparent, reusable and updatable computational models

authors: 
  - prefix: Dr.
    firstname: Leading
    particle: van 
    lastname: Author
    suffix: III
    naturename: Poet Laureate
    degrees: MSc, PhD
    email: abc@def
    affiliation: [1,2]
    corresponding: TRUE
    equalcont: These authors contributed equally to this work.

  - firstname: Second
    lastname: Author
    affiliation: 2
    equalcont: These authors contributed equally to this work.

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: Department
      orgname: Organization
    address:
        street: Street
        city: City
        postcode: 100190
        state: State
        country: Country
  - number: 2
    corresponding: TRUE
    info:
      orgname: Other Organisation

keywords:
  - key
  - dictionary
  - word

pacs: 
  jel:
    - "D8"
    - "H51"
  msc:
    - "35A01"
    - "65L10"

>>>>

title: A prototype software framework for transparent, reusable and updatable computational health economic models
titlerunning: Framework for ethical computational models

# authors:
#   - name: Matthew P Hamilton
#     email: matthew.hamilton@orygen.org.au
#     address: Orygen, Parkville, Australia
#     correspondence: true
#     equal_contributor: "yes"
#   - name: Caroline X Gao
#     address: Orygen, Parkville, Australia, Centre for Youth Mental Health, University of Melbourne, Parkville, Australia and School of Public Health and Preventive Medicine, Monash University, Clayton, Australia
#     equal_contributor: "yes"
#   - name: Kate M Filia
#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
#   - name: Jana M Menssink
#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
#   - name: Sonia  Sharmin
#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
#   - name: Nic Telford
#     address: headspace National Youth Mental Health Foundation, Melbourne, Australia
#   - name: Helen Herrman
#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
#   - name: Ian B Hickie
#     address: Brain and Mind Centre, Youth Mental Health & Technology, Faculty of Medicine & Health, The University of Sydney,  Australia
#   - name: Cathrine  Mihalopoulos
#     address: Deakin Health Economics, Institute for Health Transformation, Deakin University, Geelong,  Australia
#   - name: Debra J Rickwood
#     address: Faculty of Health, University of Canberra, Australia and headspace National Youth Mental Health Foundation, Melbourne, Australia
#   - name: Patrick D McGorry
#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
#   - name: Sue M Cotton
#     address: Orygen, Parkville, Australia and Centre for Youth Mental Health, University of Melbourne, Parkville, Australia
authors: 
  - firstname: Matthew
    particle: P 
    lastname: Hamilton
    email: matthew.hamilton1@monash.edu
    affiliation: [1,2]
    corresponding: TRUE
  # - prefix: Mr.
    #suffix: III
    #naturename: Poet Laureate
    # degrees: MSc #, PhD
    #equalcont: These authors contributed equally to this work.

  - firstname: Caroline
    lastname: Gao
    #     email: caroline.gao@orygen.org.au
    affiliation: [2,3,1]

  - firstname: Glen
    lastname: Wiesner
    #     email: glen.wiesner@heartfoundation.org.au
    affiliation: [4]

  - firstname: Kate  
    particle: M
    lastname: Filia
    #     email: kate.filia@orygen.org.au
    affiliation: [2,3]

  - firstname: Jana
    particle: M
    lastname: Menssink
    #     email: jana.menssink@orygen.org.au
    affiliation: [2,3]

  - firstname: Petra
    lastname: Plencnerova
    #     email: pplencnerova@headspace.org.au
    affiliation: [5]

  - firstname: David  
    lastname: Baker
    #     email: david.baker@orygen.org.au
    affiliation: [2,3]

  - firstname: Patrick 
    particle: D 
    lastname: McGorry
    #     email: pat.mcgorry@orygen.org.au
    affiliation: [2,3]

  - firstname: Alexandra  
    lastname: Parker
    #     email: alex.parker@vu.edu.au
    affiliation: [6,3]

  - firstname: Jonathan  
    lastname: Karnon
    #     email: jonathan.karnon@flinders.edu.au
    affiliation: [7]

  - firstname: Sue
    particle: M
    lastname: Cotton
    #     email: sue.cotton@orygen.org.au
    affiliation: [2,3]

  - firstname: Cathrine
    lastname: Mihalopoulos
    #     email: cathy.mihalopoulos@deakin.edu.au
    affiliation: [1]

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: School of Public Health and Preventive Medicine
      orgname: Monash University
    address:
        #street: "553 St Kilda Road"
        city: Melbourne
        #postcode: 3004
        #state: Victoria
        country: Australia
  - number: 2
    corresponding: FALSE
    info:
      orgname: Orygen
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
        #state: Victoria
        country: Australia
  - number: 3
    corresponding: FALSE
    info:
      orgdiv: Centre for Youth Mental Health
      orgname: The University of Melbourne
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
    #   state: Victoria
        country: Australia
  - number: 4
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Heart Foundation      
    address:
     #   street: "2/850 Collins St"
        city: Docklands
        # postcode: 3008
     #   state: Victoria
        country: Australia
  - number: 5
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: headspace National Youth Mental Health Foundation   
    address:
    #  #   street: "485 La Trobe St"
        city: Melbourne
    #     postcode: 3000
    #  #   state: Victoria
        country: Australia     
  - number: 6
    corresponding: FALSE
    info:
      orgdiv: Institute for Health and Sport
      orgname: Victoria University 
    address:
    #  #   street: "70/104 Ballarat Rd"
        city: Footscray
    #     postcode: 3011
    #  #   state: Victoria
        country: Australia 
      # 
  - number: 7
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Flinders University   
    address:
    #     # street: "182 Victoria Square"     
        city: Adelaide
    #     postcode: 5000
    #  #   state: South Australia
        country: Australia 
keywords:  
  - computational models
  - ethics of modelling
  - health economics
  - mental disorders
  - open-source models
  - software frameworks

pacs: 
  jel:
    - "C63"
    - "C88"
    - "I10"
  msc:
    - "91-08"
